### 2008-12-18 talk/ecoop2009/jitgen.tex
kill a footnote, add a reference
answer to a comment, insert another one, fix a typo

Let us look at an example. Figure \ref{fig:tlc-main} shows parts of the
main-loop of the TLC interpreter (in slightly simplified form). The static
arguments of this functions would typically be the \lstinline{code} argument
(containing the bytecode as a string), the \lstinline{pc} argument (containing
the initial program counter) and the \lstinline{pool} argument (containing the
constant pool). The \lstinline{args} argument is dynamic since it contains the
user-input of the interpreted function. Since the \lstinline{while} loop and the
contained conditions depend only on static arguments it will typically be
unrolled by a partial evaluator.

@@

\subsubsection{Hints}

>>>>

Let us look at an example. Figure \ref{fig:tlc-main} shows parts of the
main-loop of the TLC interpreter (in slightly simplified form). The static
arguments of this functions would typically be the \lstinline{code} argument
(containing the bytecode as a string \anto{what about using array of bytes instead of string? For .NET/JVM people, there is a strong difference between the twos}), the \lstinline{pc} argument (containing
the initial program counter) and the \lstinline{pool} argument (containing the
constant pool). The \lstinline{args} argument is dynamic since it contains the
user-input of the interpreted function. Since the \lstinline{while} loop and the
contained conditions depend only on static arguments it will typically be
unrolled by a partial evaluator.

@@

\subsection{Hints}
